Self Regulation Ontology Retest Analyses

### 2018-03-15 code/SRO_Retest_Analyses.Rmd
refactoring

@@

@@

```{r}
#Create df of point estimate reliabilities
numeric_cols = c()

rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
                     icc = rep(NA, length(numeric_cols)),
                     pearson = rep(NA, length(numeric_cols)),
                     partial_eta_sq = rep(NA, length(numeric_cols)),
                     sem = rep(NA, length(numeric_cols)),
                     var_subs = rep(NA, length(numeric_cols)),
                     var_ind = rep(NA, length(numeric_cols)),
                     var_resid = rep(NA, length(numeric_cols)))

@@

```{r warning=FALSE}
t1_2_difference = data.frame()

t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1
```

```{r warning=FALSE}
t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
```

```{r echo=FALSE}
rm(test_comp_date, retest_comp_date, comp_dates)
```

```{r}
mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)

data.frame(estimate=coef(summary(mod))["days_btw","Estimate"], tval=coef(summary(mod))["days_btw","t value"])
```

```{r warning=FALSE, message=FALSE}
tmp = t1_2_difference %>%
  group_by(sub_id) %>%
  summarise(mean_diff = mean(difference, na.rm=T),
            days_btw = unique(days_btw))

tmp %>%
  ggplot(aes(days_btw, mean_diff))+
  geom_point()+
  theme_bw()+
  xlab("Days between completion")+
  ylab("Mean standardized difference between two time points")+
  geom_smooth(method="lm")
```

```{r warning=FALSE, message=FALSE}
summary(lm(mean_diff ~ days_btw, data=tmp))
```

### Task level

For each variable does the average difference between two time points vary by the average number of days between the two time points? No. The slopes of these lines or the interaction is not significant.

```{r warning=FALSE, message=FALSE}
t1_2_difference <- t1_2_difference %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>% 
  mutate(task = ifelse(grepl("survey",dv), "survey","task"),
           task = ifelse(grepl("holt",dv), "task", task))

# summary(lmer(difference ~ days_btw + (task_name|sub_id), t1_2_difference))

t1_2_difference %>%
  mutate(task = ifelse(grepl("survey",dv), "survey","task"),
           task = ifelse(grepl("holt",dv), "task", task)) %>%
  group_by(dv) %>%
  summarise(mean_diff = mean(difference),
            mean_days_btw = mean(days_btw),
            task = unique(task)) %>%
  ggplot(aes(mean_days_btw, mean_diff, color=task))+
  geom_point()+
  theme_bw()+
  geom_smooth(method="lm")+
  xlab("Average days between completion")+
  ylab("Average difference between time points")+
  theme(legend.title = element_blank())
```

```{r}
tmp = t1_2_difference %>%
  group_by(dv) %>%
  summarise(mean_diff = mean(difference),
            mean_days_btw = mean(days_btw),
            task = unique(task))

summary(lm(mean_diff ~ mean_days_btw*task, tmp))
```

>>>>

```{r}
rm(test_comp_date, retest_comp_date, comp_dates)
```

@@

```{r warning=FALSE}
numeric_cols = c()

t1_2_difference = data.frame()

t1_2_difference$difference = as.data.frame(t1_2_difference$difference)$V1

t1_2_difference = t1_2_difference %>% separate(dv, c("task", "dv"), sep="\\.")
```

```{r}
retest_task_comp_times = read.csv(paste0(retest_data_path, 'Local/retest_task_completion_times.csv'))
test_task_comp_times = read.csv(paste0(retest_data_path, 'Local/test_task_completion_times.csv'))
task_comp_times = merge(retest_task_comp_times, test_task_comp_times, by=c('worker_id','task'))
rm(retest_task_comp_times, test_task_comp_times)
task_comp_times = task_comp_times %>%
  select(-X.x, -X.y) %>%
  mutate(finish_day.x = as.Date(finish_day.x),
         finish_day.y = as.Date(finish_day.y),
         days_btw = finish_day.x-finish_day.y) %>%
  rename(sub_id=worker_id)
```

```{r warning=FALSE}
t1_2_difference = merge(t1_2_difference, task_comp_times[,c('sub_id', 'task','days_btw')], by=c('sub_id', 'task'))
```

```{r echo=FALSE}
rm(task_comp_times)
```

```{r}
mod = lmer(difference ~ dv + scale(days_btw) + (1|sub_id), data = t1_2_difference)

data.frame(estimate=coef(summary(mod))["scale(days_btw)","Estimate"], tval=coef(summary(mod))["scale(days_btw)","t value"])
```

```{r warning=FALSE, message=FALSE}
tmp = t1_2_difference %>%
  group_by(sub_id, task) %>%
  summarise(mean_diff = mean(difference, na.rm=T),
            sem_diff = sem(difference),
            days_btw = unique(days_btw))
tmp %>%
  ggplot(aes(days_btw, mean_diff))+
  geom_point()+
  geom_errorbar(aes(ymin = mean_diff-(1.96*sem_diff), ymax = mean_diff+(1.96*sem_diff)))+
  theme_bw()+
  xlab("Days between completion")+
  ylab("Mean standardized difference between two time points")+
  geom_smooth(method="lm")+
  theme(legend.position = 'none')
```

```{r warning=FALSE, message=FALSE}
summary(lm(mean_diff ~ scale(days_btw), data=tmp))
```

### Measure level

For each variable does the average difference between two time points vary by the average number of days between the two time points?

The average number of days between two measurements would be the same for all measures with current way of coding the days between completion. Even if I were to go in and see if there is a way to figure out the exact day of completion the change would not be more than 7 days since we gave subjects a week to complete.

So if you regress the average difference for each measure on average delay between two measurements you are regressing a vector with varying numbers on a vector of same values, like a t test asking if the mean of the varying column, in this case the average difference score, is different than the unique value in the single value column, i.e. the average delay between two time points (Note that this should be true in theory but in practice since for each measure there might subjects for whom the dv could not be calculated there might be >1 unique values for the average delay between the two time points). This analysis is not meaningful.

Plus what you would be interested (y) is not exactly the difference between the measurements from two time points but rather the reliability of each measure.

@@

```{r}
#Create df of point estimate reliabilities
rel_df <- data.frame(spearman = rep(NA, length(numeric_cols)),
                     icc = rep(NA, length(numeric_cols)),
                     pearson = rep(NA, length(numeric_cols)),
                     partial_eta_sq = rep(NA, length(numeric_cols)),
                     sem = rep(NA, length(numeric_cols)),
                     var_subs = rep(NA, length(numeric_cols)),
                     var_ind = rep(NA, length(numeric_cols)),
                     var_resid = rep(NA, length(numeric_cols)))

@@
